---
title: "606 Model prediction and evaluation assignment 8"
author: "abebaw M"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE,message=FALSE}
knitr::opts_chunk$set(root.dir = "C:/Users/abeba/IAF 606")
```


```{r library,echo=FALSE}
library(sjlabelled)
library(dplyr)
library(mosaic)
library(sjPlot)
library(psych)
library(sjmisc)
library(naniar)
library(car)
library(visdat)
library(UpSetR)
library(magrittr)
library(stargazer)
library(arsenal)
library(descr)
library(summarytools)
library(jtools)
library(kableExtra)
library(caTools)
library(pROC)
library(tidyverse)
```

```{r}
mydata <- read.csv("C:/Users/abeba/IAF 606/diabetes_new_df.csv",header = T)
```

```{r}
mydata2 <- mydata %>% mutate(binary_readmitted=ifelse(Readmitted=="EarlyReadmitted",1,0))
```

*Splitting the data set into train and test data*

```{r}
set.seed(123)
sample = sample.split(mydata2,SplitRatio = 0.70)
train =subset(mydata2,sample ==TRUE)
test=subset(mydata2, sample==FALSE)
dim(test)
dim(train)
```

# Final model
```{r}
glm_Final <- glm(binary_readmitted ~ -Readmitted + Discharge + Race + Admit + Med_spec +
                   Time_hosp + Age + Diag + HbA1c + Age:Med_spec + Diag:Discharge + Race:Discharge +
                  Discharge:Time_hosp + Admit:Diag + Admit:Age + Time_hosp:Med_spec + Time_hosp:Diag + 
                   Med_spec:Discharge + Med_spec:Diag + HbA1c:Diag + HbA1c:Med_spec, family = binomial, data= mydata2, 
                  na.action=na.exclude)
summary(glm_Final) 
```

```{r}
Anova(glm_Final)
```


# Calculate Pseudo R2
```{r}
#install.packages("DescTools")
library(DescTools)

glm_Final %>%
  PseudoR2()
```

# Calculate average marginal effects (AME)
```{r}
#install.packages("margins")
library(margins)

glm_Final %>%
  margins() %>%
  summary()
```
```{r}
predicted_probability_default = predict(glm_Final, newdata = test, type = "response")
```

# Predict probability using logistic regression (where the target variable is a binary outcome)
```{r}
test <- test %>% 
  mutate(predicted_probability_default = predict(glm_Final, newdata = test, type = "response")) %>% 
  mutate(predicted_default = if_else(predicted_probability_default>0.5, 1, 0))
```
# Confusion Matrix
```{r}
library(caret)
confusionMatrix(as.factor(test$predicted_default), as.factor(test$binary_readmitted), positive = "1")
```

# ROC Curve and AUC
```{r}
library(cutpointr)

roc <- roc(test, x= predicted_probability_default, class = binary_readmitted, pos_class = 1, neg_class = 0)

plot(roc)
```
# Auc value 
```{r}
auc(roc)
```


```{r}
plot(roc) + 
  geom_line(data = roc, color = "red") + 
  geom_abline(slope = 1) + 
  labs(title = "ROC Curve for Logistic Regression")
```
# After determining the best model with the maximum ROC, 
# How to obtain the optimal cutoff to maximize accuracy or the sum of sensitivity and specificity
```{r}
cutpointr(test, x= predicted_probability_default, class = binary_readmitted, pos_class = 1, neg_class = 0, 
          method = maximize_metric, metric = accuracy, na.rm = TRUE)
```
```{r}
cutpointr(test, x= predicted_probability_default, class = binary_readmitted, pos_class = 1, neg_class = 0, 
          method = maximize_metric, metric = sum_sens_spec, na.rm = TRUE)
```

```{r}
RMSE       = mean((test$binary_readmitted - predicted_probability_default)^2)
RMSE
```


*If the cutting point based on the optimal_cutting method above approximately 0.1*
*the prediction of readmission  as shown below*
**Finding model predictions based on test set**
```{r}
glm_probs = predict(glm_Final, test, type="response")
```

```{r}
head(glm_probs, 10)
```


```{r}
glm_pred=rep("Other", 23328)
glm_pred[glm_probs>.1] = "Earlyreadmitted"
mytable = table(glm_pred,test$binary_readmitted)
mytable
```

**Efficiency/accuracy measure**

```{r}
efficiency <- sum(diag(mytable))/sum(mytable)
efficiency
```

**Plotting area under curve**

```{r}
roc(binary_readmitted~glm_Final$fitted.values, data = mydata2, plot = TRUE, main = "ROC CURVE", col= "blue")
```


**Calculating auc measure**

```{r}
auc(binary_readmitted~glm_Final$fitted.values, data = mydata2)
```
**Extracting true/false negatives/positives from confusion matrix**

```{r}
TP <- mytable[1, 1]
TN <- mytable[2, 2] 
FP <- mytable[1, 2]
FN <- mytable[2, 1]
```

```{r}
#calculating correct classification rate
rate <- (TP + TN) / (TP + TN + FP + FN)
rate <- round(rate, 4)*100
rate
```
**Quantitative analysis for paper model**

```{r}
precision <- TP/(TP + FP)
cat('Precision:', precision)
cat("\n")  
specificity <- TN/(TN + FP)
cat('Specificity:', specificity)
cat("\n")  
sensitivity <- TP/(TP + FN)
cat('Sensitivity:', sensitivity)
cat("\n")  
F1_Score <- 2*TP/(2*TP + FP + FN)
cat("F1_Score:", F1_Score)
cat("\n")  
J = sensitivity + specificity - 1
cat('J:', J)
```

